Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-05-28 publication_materials/ms_rbc.tex
Time evolution.
Intro.

Others have turned to studying quasilinear systems.
The quasilinear approximation starts with a decomposition of all variables into a background and perturbations about this background.
This approximation neglects the nonlinear interactions between perturbations which would otherwise modify the perturbations themselves \cite{marston2016}.
This renders the perturbation equations linear.
Although the quasilinear approximation greatly simplifies the problem, an additional condition must be imposed to determine the amplitude of the perturbations.
In \citet{Beaume_2015}, researchers compute ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. 
They assume the background velocity evolves on a slow time scale, and, to determine the perturbation amplitudes, they require marginal stability at each timestep.
% A similar strategy is employed by \citet{michel_chini_2019} to study acoustic streaming.
% In that work, an analytic expression for the first-order perturbation's amplitude is found by deriving a solvability condition.
This quasilinear approach, which relies on multi-scale arguments in conjunction with a marginal stability constraint, is generalized by \citet{Chini_ql}.
Studying two somewhat generic systems, researchers observe the interdependent evolution of a background state and its perturbations within a marginally-stable manifold.

In this paper we employ the same strategy to the more complicated Rayleigh-B\'{e}nard convection problem.
In Section~\ref{sec:model} we recall the underlying equations, and in Section~\ref{sec:evolution} we outline how we evolve the background temperature profile while maintaining marginal stability.
Section~\ref{sec:properties} pertains to the properties of the marginally-stable thermal equilibria, in particular how the Nusselt number and characteristic wavenumbers vary with the Rayleigh number.
Finally, we analyze the results of simulations initialized with marginally-stable thermal equilibria in Section~\ref{sec:sims}, and conclude in Section~\ref{sec:Discussion}.

@@

To initialize our calculations, we construct a marginally-stable initial temperature profile $\overline{T}(z, t=0)$ whose equation is given in Appendix~\ref{sec:initial_profile}. 
We use \eq{EQ:T0_IVP} to evolve $\overline{T}(z, t_0)$ into a new marginally-stable profile $\overline{T}(z, t_0 + \Delta t)$.
We use a second-order, two-stage IMEX Runge-Kutta method.
The eigenfunctions and amplitudes are assumed to be constant with respect to $t$ over the timestep.
We symmetrize $\overline{T}$ by setting the coefficients of its even Chebyshev basis functions to zero at the start of each timestep.
This ensures $\overline{T}(z) = -\overline{T}(-z)$.
On every timestep, we calculate the marginally stable eigenfunctions and their amplitude $A$.
It is essential that we pick the correct eigenfunction amplitude when calculating the advective term to maintain marginal stability.
We will now illustrate our method of finding the appropriate $A$ through an example.

>>>>

Others have turned to studying quasilinear systems.
The quasilinear approximation starts with a decomposition of all variables into a background and perturbations about this background.
This approximation neglects the nonlinear interactions between perturbations which would otherwise modify the perturbations themselves \cite{marston2016}.
This renders the perturbation equations linear.
Although the quasilinear approximation greatly simplifies the problem, an additional condition must be imposed to determine the amplitude of the perturbations.
The simplest approach is to initialize the perturbations to low amplitude, and evolve them together with the background (this is, e.g., the approach of \cite{marston2016} and many others).
A different approach was taken in \citet{Beaume_2015}, which computes ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. 
They assume the background velocity evolves on a slow time scale, and, to determine the perturbation amplitudes, they require marginal stability at each timestep.
% A similar strategy is employed by \citet{michel_chini_2019} to study acoustic streaming.
% In that work, an analytic expression for the first-order perturbation's amplitude is found by deriving a solvability condition.
This quasilinear approach, which relies on multi-scale arguments in conjunction with a marginal stability constraint, is generalized by \citet{Chini_ql}.
Studying two somewhat generic systems, researchers observe the interdependent evolution of a background state and its perturbations within a marginally-stable manifold.

In this paper we employ this strategy for the Rayleigh-B\'{e}nard convection problem.
In Section~\ref{sec:model} we recall the underlying equations, and in Section~\ref{sec:evolution} we outline how we evolve the background temperature profile while maintaining marginal stability.
Section~\ref{sec:properties} pertains to the properties of the marginally-stable thermal equilibria, in particular how the Nusselt number and characteristic wavenumbers vary with the Rayleigh number.
Finally, we analyze the results of simulations initialized with marginally-stable thermal equilibria in Section~\ref{sec:sims}, and conclude in Section~\ref{sec:Discussion}.

@@

To initialize our calculations, we construct a marginally-stable initial temperature profile $\overline{T}(z, t=0)$ whose equation is given in Appendix~\ref{sec:initial_profile}. 
Although this background temperature is marginally-stable, it is not in thermal equilibrium, so it will evolve in time.
We use \eq{EQ:T0_IVP} to evolve $\overline{T}(z, t_0)$ into a new marginally-stable profile $\overline{T}(z, t_0 + \Delta t)$.
We use a second-order, two-stage IMEX Runge-Kutta method.
The eigenfunctions and amplitudes are assumed to be constant with respect to $t$ over the timestep.
We symmetrize $\overline{T}$ by setting the coefficients of its even Chebyshev basis functions to zero at the start of each timestep.
This ensures $\overline{T}(z) = -\overline{T}(-z)$.
On every timestep, we calculate the marginally stable eigenfunctions and their amplitude $A$.
It is essential that we pick the correct eigenfunction amplitude when calculating the advective term to maintain marginal stability.
We will now illustrate our method of finding the appropriate $A$ through an example.
